### 2021-10-06 letter/letter.Rmd
remove citation
add reviewers to letter

\begin{itemize}
    \item John Matsusaka, Charles F. Sexton Chair in American Enterprise, Marshall School of Business, University of Southern California. Professor Matsusaka has written extensively about the ``law of $1/n$'' and is familiar with the literature. Email: \href{mailto:matsusak@usc.edu}{matsusak@usc.edu}.
    \item Neil Malhotra, Edith M. Cornell Professor of Political Economy, Graduate School of Business, Stanford University. Professor Malhotra has written a fundamental article about the ``law of $1/n$''. Email: \href{mailto:neilm@stanford.edu}{neilm@stanford.edu}.
    \item David M. Primo, Ani and Mark Gabrellian Professor, Department of Political Science, University of Rochester. Professor Primo has argued about the existence of a ``reverse law of $1/n$'' and has several papers on the topic. Email: \href{mailto:david.primo@rochester.edu}{david.primo@rochester.edu}.
    \item Mia Costa, Assistant Professor, Department of Government, Dartmouth College. Professor Costa has experience with meta-analysis and research methods. Email: \href{mailto:mia.costa@dartmouth.edu}{mia.costa@dartmouth.edu}.
\end{itemize}

To the best of our knowledge, none of the above-suggested persons have any conflict of interest, financial or otherwise.

>>>>

\begin{itemize}
    \item Claudio Ferraz. Professor of Economics at the Vancouver School of Economics, University of British Columbia. Email: \url{claudio.ferraz@ubc.ca}.
    \item Thomas Fujiwara. Associate Professor of Economics and International Affairs, Princeton University. Email: \url{fujiwara@princeton.edu}
    \item F. Daniel Hidalgo. Cecil and Ida Green Associate Professor of Political Science, Massachusetts Institute of Technology. Email: \url{dhidalgo@mit.edu}.
    \item Guillermo Toral. Assistant Professor of Political Science, Vanderbilt University. Email: \url{guillermo.toral@vanderbilt.edu}.
\end{itemize}

To the best of our knowledge, none of the above-suggested persons have any conflict of interest, financial or otherwise. All of them have written extensively about public service provision and government accountability in Brazil using modern causal inference methods.
